Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-15 doc/mc-paper.tex

We implemented the three programs illustrated in
Figure~\ref{fig:chain} to supplement the knowledge compiler \dfour{}.
The proof generator and proof checker were written in C/C++, while the
ring evaluator was written in Python.\footnote{The programs are
available at \texttt{https://github.com/rebryant/crat}.}  The proof
generator uses \cadical{}~\cite{biere-cadical-2019} as its SAT solver.  To convert proof steps
back into hinted CRAT clause additions, the generator can use either
its own RUP proof generator, or it can invoke \dtrim{}~\cite{RAT}.
The latter yields shorter proofs and scales well to large proofs, but
each invocation has a high startup cost.  We therefore set a threshold
of 1000 clauses in the SAT problem for using \dtrim{}.

>>>>

We implemented the three programs illustrated in
Figure~\ref{fig:chain} to supplement the knowledge compiler \dfour{}.
The proof generator and proof checker were written in C/C++, while the
ring evaluator was written in Python.\footnote{The programs are
available at \url{https://github.com/rebryant/crat}.}  The proof
generator uses \cadical{}~\cite{biere-cadical-2019} as its SAT solver.  To convert proof steps
back into hinted CRAT clause additions, the generator can use either
its own RUP proof generator, or it can invoke \dtrim{}~\cite{RAT}.
The latter yields shorter proofs and scales well to large proofs, but
each invocation has a high startup cost.  We therefore set a threshold
of 1000 clauses in the SAT problem for using \dtrim{}.
